Case study validations of automatic bullet matching

### 2018-10-10 index.Rmd
Transition, additional citations

\svp{Commonly, approaches derived from 3D surface measurements use some features which are developed to mimic the perception of FTEs\citep{luAutomatedBulletIdentification2014}. Class characteristics, which are shared by a group of firearms with the same rifling design, manufacturer, and tooling process, are typically evaluated first, as a mismatch on class charcteristics is sufficient to conclude that two samples do not match. Automated approaches to estimation of width of the land engraved area and twist angle were described in \citet{chuPilotStudyAutomated2010}. Individual characteristics, which are not shared by all members of a class, can also be automatically assessed from 3D surface measurements; in some cases, these features mimic features used by FTEs during image analysis. One of the most common features used to assess the strength of a match based on individual characteristics is the cross-correlation function (ccf), which is described in several studies \citep{maNISTBulletSignature2004, vorburgerApplicationsCrosscorrelationFunctions2011, chuPilotStudyAutomated2010}. Additional features proposed for assessing match strength also include Signature Distance \citep{maNISTBulletSignature2004} and automatically determined Consecutive Matching Striae \citep{chuAutomaticIdentificationBullet2013}.}

### Need to transition to explanation of the match algorithm...
In the \svp{matching algorithm proposed in \citet{aoas},} similarity of bullet land engraved areas is evaluated based on 3d topographic scans of land engraved areas (LEAs). From each land engraved area a signature is derived by

@@

Quantitative features describing the similarity of two signature are extracted. Features include characteristics of the signature that firearms and toolmark examiners base their visual assessment on, such as \svp{striae depth}, number of matching striae, and the number of consecutively matching striae (CMS). We also include statistical features, such as cross-correlation and Euclidean distance between the signatures. 
```{r, eval = F}
# TODO: Add correlation and euclidian distance pictures?
```

@@

The algorithm in \citet{aoas} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. Set 173 was originally published as Hamby set 44\svp{, but was mislabeled.} \svp{Probably need to mention that the NIST scans have a different resolution, which may affect how the results generalize?}

>>>>

\svp{Commonly, approaches derived from 3D surface measurements use some features which are developed to mimic the perception of FTEs\citep{luAutomatedBulletIdentification2014}. Class characteristics, which are shared by a group of firearms with the same rifling design, manufacturer, and tooling process, are typically evaluated first, as a mismatch on class charcteristics is sufficient to conclude that two samples do not match. Automated approaches to estimation of width of the land engraved area and twist angle were described in \citet{chuPilotStudyAutomated2010}. Individual characteristics, which are not shared by all members of a class, can also be automatically assessed from 3D surface measurements; in some cases, these features mimic features used by FTEs during image analysis. One of the most common features used to assess the strength of a match based on individual characteristics is the cross-correlation function (ccf), which is described in several studies \citep{maNISTBulletSignature2004, vorburgerApplicationsCrosscorrelationFunctions2011, chuPilotStudyAutomated2010}. Additional features proposed for automatically assessing match strength also include signature distance \citep{maNISTBulletSignature2004}, striae depth and width \citep{ComputerIdentificationBullets1978}, and consecutive matching striae \citep{chuAutomaticIdentificationBullet2013}.}

In the \svp{matching algorithm proposed in \citet{aoas}, many of the features described above are combined to produce a similarity score} based on 3d topographic scans of land engraved areas (LEAs). From each land engraved area a signature is derived by

@@

Quantitative features describing the similarity of two signature are extracted. Features include characteristics of the signature that firearms and toolmark examiners base their visual assessment on, such as \svp{striae depth}, number of matching striae, and the number of consecutively matching striae (CMS). We also include statistical features, such as cross-correlation and Euclidean distance between the signatures.

@@

The algorithm in \citet{aoas} is trained on scans from Hamby sets 252 and 173 made available through \citet{nist}. Set 173 was originally published as Hamby set 44\svp{, but was mislabeled.} \svp{The scans used to fit the model were taken at a resolution of \svp{Probably need to mention that the NIST scans have a different resolution, which may affect how the results generalize?}
